---
title: "VALGANCICLOVIR: 40-59 mL/min, 450 mg/j"
author: "Hamza Sayadi"
date: "2024-03-27"
output: html_document
---

#Loading library
```{r}
library(mrgsolve)
library(tidyverse)
library(tidymodels)
library(embed)
library(skimr)
library(PKNCA)
library(truncnorm)
library(mapbayr)
library(Pmetrics)
library(writexl)
library(readxl)
library(GGally)
library(tableone)
library(blandr)
library(xgboost)
```

#Data_set
```{r}
library(readxl)
data_40_59_dvp_ML <- read_excel("C:/Users/hamza/Desktop/valganciclovir/data 2 modèles pour dvp ML/data_40_59_dvp_ML.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))
```


#Filter the 1st and 99th percentiles
```{r}
quantiles <- quantile(data_40_59_dvp_ML$auc, probs = c(0.01, 0.99))

valgan_40_59_ml <- data_40_59_dvp_ML %>%
  filter(auc > quantiles[1], auc < quantiles[2])
 
valgan_40_59_ml %>% ggplot(aes(x = auc)) + 
  geom_histogram() + 
  labs(title = "Distribution of the simulated AUC at steady state", x = "'AUC valganciclovir")+ 
  theme_bw()
```

```{r}
skim(valgan_40_59_ml)
```


#Data splitting 
```{r}
set.seed(1234)
valgan_split_40_59 <- initial_split(valgan_40_59_ml, strata = auc, prop=3/4) 
valgan_ml_train_40_59  <- training(valgan_split_40_59 ) 
valgan_ml_test_40_59  <- testing(valgan_split_40_59 )

```


```{r}
skim(valgan_ml_test_40_59)
```

```{r}
skim(valgan_ml_train_40_59)
```


#Xgboost C0 à C12 + Clcr
```{r}
valgan_ml_rec_2_1  <- recipe(auc ~ ., data = valgan_ml_train_40_59) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT, conc_time_13:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors()) 

valgan_ml_rec_prep_2_1 <-  prep(valgan_ml_rec_2_1)

valgan_train_recipe_2_1 <- bake(valgan_ml_rec_prep_2_1, new_data = NULL)
valgan_test_recipe_2_1 <- bake(valgan_ml_rec_prep_2_1, new_data = valgan_ml_test_40_59)
```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_2_1 <- workflow() %>%
  add_recipe(valgan_ml_rec_2_1) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_40_59)

set.seed(345)
tune_xgb_2_1 <- tune_grid(
  xgb_wf_2_1,
  resamples = folds,
  grid = 60
)
 
autoplot(tune_xgb_2_1, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_2_1)
```


```{r}
best_rmse_xgb_2_1 <- select_best(tune_xgb_2_1, "rmse")
```

```{r}
final_xgb_2_1 <- finalize_model(
  xgb_spec,
  best_rmse_xgb_2_1
)
```

```{r}
final_wf_xgb_2_1 <- workflow() %>%
  add_recipe(valgan_ml_rec_2_1) %>%
  add_model(final_xgb_2_1)

set.seed(456)
folds_cv <- vfold_cv(valgan_ml_train_40_59, strata = auc) 

set.seed(123)
xgb_rs_2_1 <- fit_resamples (object = final_wf_xgb_2_1, resamples = folds_cv, control = control_resamples(verbose=T, save_pred=T))
```


```{r}
xgb_rs_2_1 %>% collect_metrics()
```

```{r}
xgb_rs_2_1 %>%
  collect_predictions() %>%
  ggplot(mapping = aes(x = .pred, y = auc)) + 
  geom_point() +
  geom_smooth(method=lm) 
```

```{r}
fit_workflow_2_1 <- fit(final_wf_xgb_2_1, valgan_ml_train_40_59)
```


##Validation test
```{r}
final_res_2_1 <- final_wf_xgb_2_1 %>% 
  last_fit(valgan_split_40_59)  
```

```{r}
final_res_2_1 %>% collect_metrics()
```

```{r}
final_res_predictions_2_1 <- final_res_2_1%>% collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_2_1 %>% summarise(biais_rel = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
final_res_predictions_2_1 %>%
  ggplot(mapping = aes(x =AUC_pred, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") + 
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +
  theme_bw()
```

```{r}
final_res_predictions_2_1 %>%
  ggplot(mapping = aes(x = AUC_pred, y = AUC_pred - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") + 
  labs(
    x = "Bias AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
library(vip)

xgb_fit <- extract_fit_parsnip(final_res_2_1)

vip(xgb_fit, geom = "point", num_features = 10)
```




#Xgboost C4 + C12 + Clcr
```{r}
valgan_ml_rec_2_2  <- recipe(auc ~ ., data = valgan_ml_train_40_59) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT,conc_time_0:conc_time_3, conc_time_5:conc_time_11, conc_time_13:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors()) 

valgan_ml_rec_prep_2_2 <-  prep(valgan_ml_rec_2_2 )


valgan_train_recipe_2_2 <-bake(valgan_ml_rec_prep_2_2, new_data = NULL)
valgan_test_recipe_2_2 <-bake(valgan_ml_rec_prep_2_2, new_data = valgan_ml_test_40_59)

```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_2_2 <- workflow() %>%
  add_recipe(valgan_ml_rec_2_2) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_40_59)

set.seed(345)
tune_xgb_2_2 <- tune_grid(
  xgb_wf_2_2,
  resamples = folds,
  grid = 60
)

autoplot(tune_xgb_2_2, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_2_2)
```

```{r}
best_rmse_xgb_2_2 <- select_best(tune_xgb_2_2, "rmse")
```

```{r}
final_xgb_2_2 <- finalize_model(
  xgb_spec,
  best_rmse_xgb_2_2
)
```


```{r}

final_wf_xgb_2_2 <- workflow() %>%
  add_recipe(valgan_ml_rec_2_2) %>%
  add_model(final_xgb_2_2)

set.seed(456)
folds_cv <- vfold_cv(valgan_ml_train_40_59, strata = auc) 

set.seed(123)
xgb_rs_2_2 <- fit_resamples (object = final_wf_xgb_2_2, 
                             resamples = folds_cv, 
                             control = control_resamples(verbose=T, save_pred=T))
```


```{r}
xgb_rs_2_2 %>% collect_metrics()
```

```{r}
xgb_rs_2_2 %>%
  collect_predictions() %>%
  ggplot(mapping = aes(x = .pred, y = auc)) + 
  geom_point() +
  geom_smooth(method=lm) 
```

```{r}
fit_workflow_2_2 <- fit(final_wf_xgb_2_2, valgan_ml_train_40_59)
```


##Validation test
```{r}
final_res_2_2 <- final_wf_xgb_2_2 %>% 
  last_fit(valgan_split_40_59)  
```

```{r}
final_res_2_2 %>% collect_metrics()
```

```{r}
final_res_predictions_2_2 <- final_res_2_2 %>% 
  collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_2_2 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
final_res_predictions_2_2 %>%
  ggplot(mapping = aes(x =AUC_pred, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +
  theme_bw()
```

```{r}
final_res_predictions_2_2 %>%
  ggplot(mapping = aes(x = AUC_pred, y = AUC_pred - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Reference AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +
  theme_bw()
```

```{r}
library(vip)

xgb_fit <- extract_fit_parsnip(final_res_2_2)

vip(xgb_fit, geom = "point", num_features = 5)
```

```{r}
 saveRDS(fit_workflow_2_2, file = "C:/Users/hamza/Desktop/valganciclovir/algo/xgboost_40-59_2_points_070324.rds")
```




#Xgboost C3 + C4 + C12 + Clcr
```{r}
valgan_ml_rec_2_3  <- recipe(auc ~ ., data = valgan_ml_train_40_59) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT, conc_time_0:conc_time_2, conc_time_5:conc_time_11, conc_time_13:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors()) 

valgan_ml_rec_prep_2_3 <-  prep(valgan_ml_rec_2_3 )


valgan_train_recipe_2_3 <-bake(valgan_ml_rec_prep_2_3, new_data = NULL)
valgan_test_recipe_2_3 <-bake(valgan_ml_rec_prep_2_3, new_data = valgan_ml_test_40_59)

```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_2_3 <- workflow() %>%
  add_recipe(valgan_ml_rec_2_3) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_40_59)

set.seed(345)
tune_xgb_2_3 <- tune_grid(
  xgb_wf_2_3,
  resamples = folds,
  grid = 60
)

autoplot(tune_xgb_2_3, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_2_3)
```

```{r}
best_rmse_xgb_2_3 <- select_best(tune_xgb_2_3, "rmse")
```

```{r}
final_xgb_2_3 <- finalize_model(
  xgb_spec,
  best_rmse_xgb_2_3
)
```


```{r}
final_wf_xgb_2_3 <- workflow() %>%
  add_recipe(valgan_ml_rec_2_3) %>%
  add_model(final_xgb_2_3)

set.seed(4567)
folds_cv <- vfold_cv(valgan_ml_train_40_59, strata = auc) 

set.seed(1234)
xgb_rs_2_3 <- fit_resamples (object = final_wf_xgb_2_3, resamples = folds_cv, control = control_resamples(verbose=T, save_pred=T))
```

```{r}
xgb_rs_2_3 %>% collect_metrics()
```

```{r}
xgb_rs_2_3 %>%
  collect_predictions() %>%
  ggplot(mapping = aes(x = .pred, y = auc)) + 
  geom_point() +
  geom_smooth(method=lm) 
```

```{r}
fit_workflow_2_3 <- fit(final_wf_xgb_2_3, valgan_ml_train_40_59)
```


##Validation test
```{r}
final_res_2_3 <- final_wf_xgb_2_3 %>% 
  last_fit(valgan_split_40_59)  
```

```{r}
final_res_2_3 %>% collect_metrics()
```

```{r}
final_res_predictions_2_3 <- final_res_2_3 %>%
  collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_2_3 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
final_res_predictions_2_3 %>%
  ggplot(mapping = aes(x =AUC_pred, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
final_res_predictions_2_3%>%
  ggplot(mapping = aes(x = AUC_pred, y = AUC_pred - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Reference AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
library(vip)

xgb_fit <- extract_fit_parsnip(final_res_2_3)

vip(xgb_fit, geom = "point", num_features = 5)
```


```{r}
 saveRDS(fit_workflow_2_3, file = "C:/Users/hamza/Desktop/valganciclovir/algo/xgboost_40-59_3_points_070324.rds")
```




#XGBOOST  C0 + C4 + C5 + Clcr
```{r}
#pre processing
valgan_ml_rec_2_3_bis  <- recipe(auc ~ ., data = valgan_ml_train_40_59) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT, conc_time_1:conc_time_3, conc_time_6:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors()) 

valgan_ml_rec_prep_2_3_bis <-  prep(valgan_ml_rec_2_3_bis )

valgan_train_recipe_2_3_bis <- bake(valgan_ml_rec_prep_2_3_bis, new_data = NULL)
valgan_test_recipe_2_3_bis <- bake(valgan_ml_rec_prep_2_3_bis, new_data = valgan_ml_test_40_59)

```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_2_3_bis <- workflow() %>%
  add_recipe(valgan_ml_rec_2_3_bis) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_40_59)

set.seed(345)
tune_xgb_2_3_bis <- tune_grid(
  xgb_wf_2_3_bis,
  resamples = folds,
  grid = 60
)

autoplot(tune_xgb_2_3_bis, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_2_3_bis)
```

```{r}
best_rmse_xgb_2_3_bis <- select_best(tune_xgb_2_3_bis, "rmse")
```

```{r}
final_xgb_2_3_bis <- finalize_model(
  xgb_spec,
  best_rmse_xgb_2_3_bis
)
```

```{r}
final_wf_xgb_2_3_bis <- workflow() %>%
  add_recipe(valgan_ml_rec_2_3_bis) %>%
  add_model(final_xgb_2_3_bis)

set.seed(456)
folds_cv <- vfold_cv(valgan_ml_train_40_59, strata = auc) 

set.seed(123)
xgb_rs_2_3_bis <- fit_resamples (object = final_wf_xgb_2_3_bis, 
                            resamples = folds_cv, 
                            control = control_resamples(verbose=T, save_pred=T))
```

```{r}
xgb_rs_2_3_bis %>% collect_metrics()
```

```{r}
xgb_rs_2_3_bis %>%
  collect_predictions() %>%
  ggplot(mapping = aes(x = .pred, y = auc)) + 
  geom_point() +
  geom_smooth(method=lm) +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)")
```

```{r}
fit_workflow_2_3_bis <- fit(final_wf_xgb_2_3_bis, valgan_ml_train_40_59)
```


##Validation Test
```{r}
final_res_2_3_bis <- final_wf_xgb_2_3_bis %>% 
  last_fit(valgan_split_40_59)  
```

```{r}
final_res_2_3_bis %>% collect_metrics()
```

```{r}
final_res_predictions_2_3_bis <- final_res_2_3_bis %>% 
  collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_2_3_bis %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
final_res_predictions_2_3_bis %>%
  ggplot(mapping = aes(x =AUC_pred, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
final_res_predictions_2_3_bis %>%
  ggplot(mapping = aes(x = AUC_pred, y = AUC_pred - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Reference AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
library(vip)

xgb_fit <- extract_fit_parsnip(final_res_2_3_bis)

vip(xgb_fit, geom = "point", num_features = 5)
```

```{r}
 saveRDS(fit_workflow_2_3_bis, file = "C:/Users/hamza/Desktop/valganciclovir/algo/xgboost_40-59_3_points_bis_070324.rds")
```



















Estimating AUC using ML algorithms on an external database (98 Caldés patients and 98 Chen patients)

#Test 1: 98 patients from the Caldés model (DFG between 40 and 59 mL/min, 450 mg once daily)

##data loading
```{r}
library(readxl)
data_Clcr_40_59_Caldés <- read_excel("C:/Users/hamza/Desktop/valganciclovir/data 2 modèles validation ML/data_Clcr_40_59_Caldés.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))
```

##Filter the 1st and 99th percentiles
```{r}
quantiles <- quantile(data_Clcr_40_59_Caldés$auc, probs = c(0.01, 0.99))

valgan_40_59_test_1 <- data_Clcr_40_59_Caldés %>%
  filter(auc > quantiles[1], auc < quantiles[2])
```

```{r}
skim(valgan_40_59_test_1)
```

##Prediction with the 2-samples algorithm (C4 and C12 + Clcr)
```{r}
fit_workflow_3_2 <- readRDS("C:/Users/hamza/Desktop/valganciclovir/algo/xgboost_40-59_2_points_070324.rds")
predictions_3_2 <- predict(fit_workflow_3_2, valgan_40_59_test_1)
```

```{r}
valgan_40_59_test_1$AUC_pred_2_points <- predictions_3_2$.pred
```

```{r}
final_predictions_3_2 <- valgan_40_59_test_1 %>% 
  mutate(bias_rel = (AUC_pred_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_3_2 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
final_predictions_3_2 %>%
  ggplot(mapping = aes(x =AUC_pred_2_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") + 
  theme_bw()
```

```{r}
#residual scatterplot
final_predictions_3_2 %>%
  ggplot(mapping = aes(x = AUC_pred_2_points, y = AUC_pred_2_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```



## Prediction with the 3-samples algorithm (C3, C4, and C12 + Clcr)
```{r}
fit_workflow_3_3 <- readRDS("C:/Users/hamza/Desktop/valganciclovir/algo/xgboost_40-59_3_points_070324.rds")
predictions_3_3 <- predict(fit_workflow_3_3, valgan_40_59_test_1)
```

```{r}
valgan_40_59_test_1$AUC_pred_3_points <- predictions_3_3$.pred
```

```{r}
final_predictions_3_3 <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_pred_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_3_3 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
final_predictions_3_3 %>%
  ggplot(mapping = aes(x =AUC_pred_3_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
final_predictions_3_3 %>%
  ggplot(mapping = aes(x = AUC_pred_3_points, y = AUC_pred_3_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```


##Prediction with the 3-samples algorithm (C0, C4, and C5 + Clcr)
```{r}
fit_workflow_3_3_bis <- readRDS("C:/Users/hamza/Desktop/valganciclovir/algo/xgboost_40-59_3_points_bis_070324.rds")
predictions_3_3_bis <- predict(fit_workflow_3_3_bis, valgan_40_59_test_1)
```

```{r}
valgan_40_59_test_1$AUC_pred_3_points_bis <- predictions_3_3_bis$.pred
```

```{r}

final_predictions_3_3_bis <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_pred_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_3_3_bis %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
final_predictions_3_3_bis %>%
  ggplot(mapping = aes(x =AUC_pred_3_points_bis, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
final_predictions_3_3_bis %>%
  ggplot(mapping = aes(x = AUC_pred_3_points_bis, y = AUC_pred_3_points_bis - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```





#Test 2: 98 patients from the Chen et al. model (GFR between 40 and 59 mL/min, 450 mg/day)
## data loading
```{r}
library(readxl)
data_40_59_Chen <- read_excel("C:/Users/hamza/Desktop/valganciclovir/data 2 modèles validation ML/data_40_59_Chen.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))
```

##Filter the 1st and 99th percentiles
```{r}
quantiles <- quantile(data_40_59_Chen$auc, probs = c(0.01, 0.99))

valgan_40_59_test_2 <- data_40_59_Chen %>%
  filter(auc > quantiles[1], auc < quantiles[2])
```

```{r}
skim(valgan_40_59_test_2)
```


##Prediction with the 2-samples algorithm (C4 and C12 + Clcr)
```{r}
predictions_4_2 <- predict(fit_workflow_3_2, valgan_40_59_test_2)
```

```{r}
valgan_40_59_test_2$AUC_pred_2_points <- predictions_4_2$.pred
```

```{r}

final_predictions_4_2 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_pred_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_4_2 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
final_predictions_4_2 %>%
  ggplot(mapping = aes(x =AUC_pred_2_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
final_predictions_4_2 %>%
  ggplot(mapping = aes(x = AUC_pred_2_points, y = AUC_pred_2_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```



##Prediction with the 3-samples algorithm (C3, C4, and C12 + Clcr)
```{r}
predictions_4_3 <- predict(fit_workflow_3_3, valgan_40_59_test_2)
```

```{r}
valgan_40_59_test_2$AUC_pred_3_points <- predictions_4_3$.pred
```

```{r}
final_predictions_4_3 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_pred_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_4_3 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
final_predictions_4_3 %>%
  ggplot(mapping = aes(x =AUC_pred_3_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
final_predictions_4_3 %>%
  ggplot(mapping = aes(x = AUC_pred_3_points, y = AUC_pred_3_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```


##Prediction with the 3-samples algorithm (C0, C4, and C5 + Clcr)
```{r}
predictions_4_3_bis <- predict(fit_workflow_3_3_bis, valgan_40_59_test_2)
```

```{r}
valgan_40_59_test_2$AUC_pred_3_points_bis <- predictions_4_3_bis$.pred
```

```{r}

final_predictions_4_3_bis <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_pred_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_4_3_bis %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
final_predictions_4_3_bis %>%
  ggplot(mapping = aes(x =AUC_pred_3_points_bis, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
final_predictions_4_3_bis %>%
  ggplot(mapping = aes(x = AUC_pred_3_points_bis, y = AUC_pred_3_points_bis - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```














Bayesian prediction using the Vezina and Lalagkas models on the 98 patients simulated from the Caldes model (valgan_40_59_test_1)

#Prediction with the Vezina et al. model
## 2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_1))

for(i in 1:nrow(valgan_40_59_test_1)) {
  conc_time_4 <- valgan_40_59_test_1$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_1$conc_time_12[i]
  Clcr <- valgan_40_59_test_1$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}


valgan_40_59_test_1$AUC_mapb_Veniza_2_points <- auc_estimated


prediction_mapb_Veniza_2_points_Ca_40_59 <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_2_points_Ca_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Veniza_2_points_Ca_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Veniza_2_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Veniza_2_points_Ca_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Veniza_2_points, y = AUC_mapb_Veniza_2_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```


#3 samples (C3, C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_1))

for(i in 1:nrow(valgan_40_59_test_1)) {
  conc_time_3 <- valgan_40_59_test_1$conc_time_3[i]
  conc_time_4 <- valgan_40_59_test_1$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_1$conc_time_12[i]
  Clcr <- valgan_40_59_test_1$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
     obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}


valgan_40_59_test_1$AUC_mapb_Veniza_3_points <- auc_estimated


prediction_mapb_Veniza_3_points_Ca_40_59 <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_Ca_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Veniza_3_points_Ca_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Veniza_3_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Veniza_3_points_Ca_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Veniza_3_points, y = AUC_mapb_Veniza_3_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```


##3 samples (C0, C4 et C5)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_1))

for(i in 1:nrow(valgan_40_59_test_1)) {
  conc_time_0 <- valgan_40_59_test_1$conc_time_0[i]
  conc_time_4 <- valgan_40_59_test_1$conc_time_4[i]
  conc_time_5 <- valgan_40_59_test_1$conc_time_5[i]
  Clcr <- valgan_40_59_test_1$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
     obs_rows(time = 0, DV = conc_time_0) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 5, DV = conc_time_5) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_1$AUC_mapb_Veniza_3_points_bis <- auc_estimated

prediction_mapb_Veniza_3_points_bis_Ca_40_59 <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_bis_Ca_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Veniza_3_points_bis_Ca_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Veniza_3_points_bis, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Veniza_3_points_bis_Ca_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Veniza_3_points_bis, y = AUC_mapb_Veniza_3_points_bis - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```




#Prediction with the Lalagkas model 
## 2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_1))

for(i in 1:nrow(valgan_40_59_test_1)) {
  
  conc_time_4 <- valgan_40_59_test_1$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_1$conc_time_12[i]
  Clcr <- valgan_40_59_test_1$Clcr[i]
  
  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_1$AUC_mapb_Lalagkas_2_points <- auc_estimated


prediction_mapb_Lalagkas_2_points_Ca_40_59 <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_2_points_Ca_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Lalagkas_2_points_Ca_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Lalagkas_2_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Lalagkas_2_points_Ca_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Lalagkas_2_points, y = AUC_mapb_Lalagkas_2_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Biais AUC (mg*h/L)") +  
  theme_bw()
```


##3 samples (C3, C4 et C12)
```{r}

auc_estimated <- numeric(length = nrow(valgan_40_59_test_1))

for(i in 1:nrow(valgan_40_59_test_1)) {
  conc_time_3 <- valgan_40_59_test_1$conc_time_3[i]
  conc_time_4 <- valgan_40_59_test_1$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_1$conc_time_12[i]
  Clcr <- valgan_40_59_test_1$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_1$AUC_mapb_Lalagkas_3_points <- auc_estimated

prediction_mapb_Lalagkas_3_points_Ca_40_59 <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_Ca_40_59 %>%
                                       summarise(relative_bias = mean(bias_rel), 
                                                 relative_rmse = sqrt(mean(bias_rel_square)),
                                                 biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
                                                 nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
                                                 n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Lalagkas_3_points_Ca_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Lalagkas_3_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Lalagkas_3_points_Ca_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Lalagkas_3_points, y = AUC_mapb_Lalagkas_3_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Biais AUC (mg*h/L)") +  
  theme_bw()
```


##3 samples (C0, C4 et C5)
```{r}

auc_estimated <- numeric(length = nrow(valgan_40_59_test_1))

for(i in 1:nrow(valgan_40_59_test_1)) {
  # Extraction des valeurs pour le patient courant
  conc_time_0 <- valgan_40_59_test_1$conc_time_0[i]
  conc_time_4 <- valgan_40_59_test_1$conc_time_4[i]
  conc_time_5 <- valgan_40_59_test_1$conc_time_5[i]
  Clcr <- valgan_40_59_test_1$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
     obs_rows(time = 0, DV = conc_time_0) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 5, DV = conc_time_5) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_1$AUC_mapb_Lalagkas_3_points_bis <- auc_estimated

prediction_mapb_Lalagkas_3_points_bis_40_59 <- valgan_40_59_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_bis_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Lalagkas_3_points_bis_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Lalagkas_3_points_bis, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Lalagkas_3_points_bis_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Lalagkas_3_points_bis, y = AUC_mapb_Lalagkas_3_points_bis - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```






Bayesian prediction by the Vezina and Lalagkas model on the 98 patients simulated from the Chen model (valgan_40_59_test_2)

#Prediction with the Vezina model
##2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_2))

for(i in 1:nrow(valgan_40_59_test_2)) {
  
  conc_time_4 <- valgan_40_59_test_2$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_2$conc_time_12[i]
  Clcr <- valgan_40_59_test_2$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
 
  auc_estimated[i] <- AUC
}


valgan_40_59_test_2$AUC_mapb_Veniza_2_points <- auc_estimated


prediction_mapb_Veniza_2_points_Ch_40_59 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_2_points_Ch_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Veniza_2_points_Ch_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Veniza_2_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Veniza_2_points_Ch_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Veniza_2_points, y = AUC_mapb_Veniza_2_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```

##3 samples (C3, C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_2))

for(i in 1:nrow(valgan_40_59_test_2)) {
  # Extraction des valeurs pour le patient courant
  conc_time_3 <- valgan_40_59_test_2$conc_time_3[i]
  conc_time_4 <- valgan_40_59_test_2$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_2$conc_time_12[i]
  Clcr <- valgan_40_59_test_2$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
     obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_2$AUC_mapb_Veniza_3_points <- auc_estimated


prediction_mapb_Veniza_3_points_Ch_40_59 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_Ch_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Veniza_3_points_Ch_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Veniza_3_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Veniza_3_points_Ch_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Veniza_3_points, y = AUC_mapb_Veniza_3_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```

##3 samples (C0, C4 et C5)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_2))

for(i in 1:nrow(valgan_40_59_test_2)) {
  conc_time_0 <- valgan_40_59_test_2$conc_time_0[i]
  conc_time_4 <- valgan_40_59_test_2$conc_time_4[i]
  conc_time_5 <- valgan_40_59_test_2$conc_time_5[i]
  Clcr <- valgan_40_59_test_2$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
     obs_rows(time = 0, DV = conc_time_0) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 5, DV = conc_time_5) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_2$AUC_mapb_Veniza_3_points_bis <- auc_estimated

prediction_mapb_Veniza_3_points_bis_Ch_40_59 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_bis_Ch_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Veniza_3_points_bis_Ch_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Veniza_3_points_bis, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Veniza_3_points_bis_Ch_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Veniza_3_points_bis, y = AUC_mapb_Veniza_3_points_bis - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Bias AUC (mg*h/L)") +  
  theme_bw()
```


#Prediction with the Lalagkas model
##2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_2))

for(i in 1:nrow(valgan_40_59_test_2)) {
  # Extraction des valeurs pour le patient courant
  conc_time_4 <- valgan_40_59_test_2$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_2$conc_time_12[i]
  Clcr <- valgan_40_59_test_2$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_2$AUC_mapb_Lalagkas_2_points <- auc_estimated

prediction_mapb_Lalagkas_2_points_Ch_40_59 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_2_points_Ch_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Lalagkas_2_points_Ch_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Lalagkas_2_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Lalagkas_2_points_Ch_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Lalagkas_2_points, y = AUC_mapb_Lalagkas_2_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black")+
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Biais AUC (mg*h/L)")+  
  theme_bw()
```

##3 samples (C3, C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_2))

for(i in 1:nrow(valgan_40_59_test_2)) {
  conc_time_3 <- valgan_40_59_test_2$conc_time_3[i]
  conc_time_4 <- valgan_40_59_test_2$conc_time_4[i]
  conc_time_12 <- valgan_40_59_test_2$conc_time_12[i]
  Clcr <- valgan_40_59_test_2$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_2$AUC_mapb_Lalagkas_3_points <- auc_estimated

prediction_mapb_Lalagkas_3_points_Ch_40_59 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_Ch_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Lalagkas_3_points_Ch_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Lalagkas_3_points, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Lalagkas_3_points_Ch_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Lalagkas_3_points, y = AUC_mapb_Lalagkas_3_points - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black")+
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Biais AUC (mg*h/L)")+  
  theme_bw()
```

##3 samples (C0, C4 et C5)
```{r}
auc_estimated <- numeric(length = nrow(valgan_40_59_test_2))

for(i in 1:nrow(valgan_40_59_test_2)) {
  conc_time_0 <- valgan_40_59_test_2$conc_time_0[i]
  conc_time_4 <- valgan_40_59_test_2$conc_time_4[i]
  conc_time_5 <- valgan_40_59_test_2$conc_time_5[i]
  Clcr <- valgan_40_59_test_2$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 450, ii = 24, ss = 1) %>%
    obs_rows(time = 0, DV = conc_time_0) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 5, DV = conc_time_5) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_40_59_test_2$AUC_mapb_Lalagkas_3_points_bis <- auc_estimated



prediction_mapb_Lalagkas_3_points_bis_Ch_40_59 <- valgan_40_59_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_bis_Ch_40_59 %>% summarise(relative_bias = mean(bias_rel), relative_rmse = sqrt(mean(bias_rel_square)),biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), n= n())))
```

```{r}
#pred scatterplot
prediction_mapb_Lalagkas_3_points_bis_Ch_40_59 %>%
  ggplot(mapping = aes(x =AUC_mapb_Lalagkas_3_points_bis, y = auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black") +
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Reference AUC (mg*h/L)") +  
  theme_bw()
```

```{r}
#residual scatterplot
prediction_mapb_Lalagkas_3_points_bis_Ch_40_59 %>%
  ggplot(mapping = aes(x = AUC_mapb_Lalagkas_3_points_bis, y = AUC_mapb_Lalagkas_3_points_bis - auc)) +
  geom_point() +
  geom_smooth(method=lm,color = "black")+
  labs(
    x = "Predicted AUC (mg*h/L)",
    y = "Biais AUC (mg*h/L)")+  
  theme_bw()
```
