---
title: 'VALGANCICLOVIR: ⩾60 mL/min, 900 mg/j'
author: "Hamza Sayadi"
---

#Loading library
```{r}
library(mrgsolve)
library(tidyverse)
library(tidymodels)
library(embed)
library(skimr)
library(PKNCA)
library(truncnorm)
library(mapbayr)
library(Pmetrics)
library(writexl)
library(readxl)
library(GGally)
library(tableone)
library(blandr)
library(xgboost)
library(vip)
```


#Data_set
```{r}
library(readxl)
data_60_120_dvp_ML <- read_excel("./data/data_60_120_dvp_ML.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))

```


#Filter the 1st and 99th percentiles
```{r}
quantiles <- quantile(data_60_120_dvp_ML$auc, probs = c(0.01, 0.99))

valgan_60_120_ml <- data_60_120_dvp_ML %>%
  filter(auc > quantiles[1], auc < quantiles[2])
 
valgan_60_120_ml %>% ggplot(aes(x = auc)) + 
  geom_histogram() + 
  labs(title = "Distribution of the simulated AUC at steady state", x = "'AUC valganciclovir") + 
  theme_bw()
```


```{r}
skim(valgan_60_120_ml)
```


#Data splitting 
```{r}
set.seed(1234)
valgan_split_60_120 <- initial_split(valgan_60_120_ml, strata = auc, prop=3/4) 
valgan_ml_train_60_120  <- training(valgan_split_60_120) 
valgan_ml_test_60_120  <- testing(valgan_split_60_120)
```



#Xgboost C0 à C12 + Clcr
```{r}
valgan_ml_rec_1_1  <- recipe(auc ~ ., data = valgan_ml_train_60_120) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT, conc_time_13:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors()) 

valgan_ml_rec_prep_1_1 <-  prep(valgan_ml_rec_1_1 )
valgan_train_recipe_1_1 <-bake(valgan_ml_rec_prep_1_1, new_data = NULL)
valgan_test_recipe_1_1 <-bake(valgan_ml_rec_prep_1_1, new_data = valgan_ml_test_60_120)
```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_1_1 <- workflow() %>%
  add_recipe(valgan_ml_rec_1_1) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_60_120)

set.seed(345)
tune_xgb_1_1 <- tune_grid(
  xgb_wf_1_1,
  resamples = folds,
  grid = 60
)

autoplot(tune_xgb_1_1, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_1_1)
```

```{r}
best_rmse_xgb_1_1 <- select_best(tune_xgb_1_1, "rmse")
```

```{r}
final_xgb_1_1 <- finalize_model(
  xgb_spec,
  best_rmse_xgb_1_1
)
```

```{r}
final_wf_xgb_1_1 <- workflow() %>%
  add_recipe(valgan_ml_rec_1_1) %>%
  add_model(final_xgb_1_1)

set.seed(456)
folds_cv <- vfold_cv(valgan_ml_train_60_120, strata = auc) 

set.seed(123)
xgb_rs_1_1 <- fit_resamples (object = final_wf_xgb_1_1, resamples = folds_cv, control = control_resamples(verbose=T, save_pred=T))
```

```{r}
xgb_rs_1_1 %>% collect_metrics()
```

```{r}
fit_workflow_1_1 <- fit(final_wf_xgb_1_1, valgan_ml_train_60_120)
```


##Validation test
```{r}
final_res_1_1 <- final_wf_xgb_1_1 %>% 
  last_fit(valgan_split_60_120)  
```

```{r}
final_res_1_1 %>% collect_metrics()
```

```{r}
final_res_predictions_1_1 <- final_res_1_1%>% collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_1_1 %>% 
summarise(biais_rel = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```

```{r}
xgb_fit <- extract_fit_parsnip(final_res_1_1)

vip(xgb_fit, geom = "point", num_features = 10)
```







#XGBOOST  C4 + C12 + Clcr
```{r}
valgan_ml_rec_1_2  <- recipe(auc ~ ., data = valgan_ml_train_60_120) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT,conc_time_0:conc_time_3, conc_time_5:conc_time_11, conc_time_13:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors())

valgan_ml_rec_prep_1_2 <-  prep(valgan_ml_rec_1_2 )

valgan_train_recipe_1_2 <-bake(valgan_ml_rec_prep_1_2, new_data = NULL)
valgan_test_recipe_1_2 <-bake(valgan_ml_rec_prep_1_2, new_data = valgan_ml_test_60_120)
```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_1_2 <- workflow() %>%
  add_recipe(valgan_ml_rec_1_2) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_60_120)

set.seed(345)
tune_xgb_1_2 <- tune_grid(
  xgb_wf_1_2,
  resamples = folds,
  grid = 60
)

autoplot(tune_xgb_1_2, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_1_2)
```

```{r}
best_rmse_xgb_1_2 <- select_best(tune_xgb_1_2, "rmse")
```

```{r}
final_xgb_1_2 <- finalize_model(
  xgb_spec,
  best_rmse_xgb_1_2
)
```

```{r}
final_wf_xgb_1_2 <- workflow() %>%
  add_recipe(valgan_ml_rec_1_2) %>%
  add_model(final_xgb_1_2)

set.seed(456)
folds_cv <- vfold_cv(valgan_ml_train_60_120, strata = auc) 

set.seed(123)
xgb_rs_1_2 <- fit_resamples (object = final_wf_xgb_1_2, 
                             resamples = folds_cv, 
                             control = control_resamples(verbose=T, save_pred=T))
```

```{r}
xgb_rs_1_2 %>% collect_metrics()
```

```{r}
fit_workflow_1_2 <- fit(final_wf_xgb_1_2, valgan_ml_train_60_120)
```


##Validation test
```{r}
final_res_1_2 <- final_wf_xgb_1_2 %>% 
  last_fit(valgan_split_60_120) 
```

```{r}
final_res_1_2 %>% collect_metrics()
```

```{r}
final_res_predictions_1_2 <- final_res_1_2 %>% collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_1_2 %>% 
summarise(relative_biais = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```









#XGBOOST  C3 + C4 + C12 + Clcr
```{r}
valgan_ml_rec_1_3  <- recipe(auc ~ ., data = valgan_ml_train_60_120) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT, conc_time_0:conc_time_2, conc_time_5:conc_time_11, conc_time_13:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors()) 

valgan_ml_rec_prep_1_3 <-  prep(valgan_ml_rec_1_3 )

valgan_train_recipe_1_3 <- bake(valgan_ml_rec_prep_1_3, new_data = NULL)
valgan_test_recipe_1_3 <- bake(valgan_ml_rec_prep_1_3, new_data = valgan_ml_test_60_120)
```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_1_3 <- workflow() %>%
  add_recipe(valgan_ml_rec_1_3) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_60_120)

set.seed(345)
tune_xgb_1_3 <- tune_grid(
  xgb_wf_1_3,
  resamples = folds,
  grid = 60
)

autoplot(tune_xgb_1_3, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_1_3)
```

```{r}
best_rmse_xgb_1_3 <- select_best(tune_xgb_1_3, "rmse")
```

```{r}
final_xgb_1_3 <- finalize_model(
  xgb_spec,
  best_rmse_xgb_1_3
)
```

```{r}
final_wf_xgb_1_3 <- workflow() %>%
  add_recipe(valgan_ml_rec_1_3) %>%
  add_model(final_xgb_1_3)

set.seed(456)
folds_cv <- vfold_cv(valgan_ml_train_60_120, strata = auc) 

set.seed(123)
xgb_rs_1_3<- fit_resamples (object = final_wf_xgb_1_3, 
                            resamples = folds_cv, 
                            control = control_resamples(verbose=T, save_pred=T))
```

```{r}
xgb_rs_1_3 %>% collect_metrics()
```

```{r}
fit_workflow_1_3 <- fit(final_wf_xgb_1_3, valgan_ml_train_60_120)
```


##Validation test
```{r}
final_res_1_3 <- final_wf_xgb_1_3 %>% 
  last_fit(valgan_split_60_120)  
```

```{r}
final_res_1_3 %>% collect_metrics()
```

```{r}
final_res_predictions_1_3 <- final_res_1_3 %>% 
  collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_1_3 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```









#XGBOOST  C3 + C4 + C6 + Clcr
```{r}
valgan_ml_rec_1_3_bis  <- recipe(auc ~ ., data = valgan_ml_train_60_120) %>%
  update_role(ID, new_role = "ID") %>% 
  step_rm(amt, CL, WT, conc_time_0:conc_time_2, conc_time_5, conc_time_7:conc_time_72) %>%
  step_YeoJohnson(contains("conc")) %>%  
  step_normalize(all_numeric_predictors()) 

valgan_ml_rec_prep_1_3_bis <-  prep(valgan_ml_rec_1_3_bis )
valgan_train_recipe_1_3_bis <- bake(valgan_ml_rec_prep_1_3_bis, new_data = NULL)
valgan_test_recipe_1_3_bis <- bake(valgan_ml_rec_prep_1_3_bis, new_data = valgan_ml_test_60_120)

```

```{r}
xgb_spec <- boost_tree(mode = "regression",
                        mtry = tune(),
                        trees = tune(),
                        min_n = tune(),
                        sample_size = tune(),
                        tree_depth = tune(),
                        learn_rate = tune()) %>% 
                          set_engine("xgboost")

xgb_wf_1_3_bis <- workflow() %>%
  add_recipe(valgan_ml_rec_1_3_bis) %>%
  add_model(xgb_spec)

set.seed(2345)
folds <- vfold_cv(valgan_ml_train_60_120)

set.seed(345)
tune_xgb_1_3_bis <- tune_grid(
  xgb_wf_1_3_bis,
  resamples = folds,
  grid = 60
)

autoplot(tune_xgb_1_3_bis, metric = "rmse",  scientific = FALSE) + 
  theme_bw() +
  ggtitle("tuning hyperparameter")
```

```{r}
show_best(tune_xgb_1_3_bis)
```

```{r}
best_rmse_xgb_1_3_bis <- select_best(tune_xgb_1_3_bis, "rmse")
```

```{r}
final_xgb_1_3_bis <- finalize_model(
  xgb_spec,
  best_rmse_xgb_1_3_bis
)
```

```{r}
final_wf_xgb_1_3_bis <- workflow() %>%
  add_recipe(valgan_ml_rec_1_3_bis) %>%
  add_model(final_xgb_1_3_bis)

set.seed(456)
folds_cv <- vfold_cv(valgan_ml_train_60_120, strata = auc) 

set.seed(123)
xgb_rs_1_3_bis <- fit_resamples (object = final_wf_xgb_1_3_bis, 
                            resamples = folds_cv, 
                            control = control_resamples(verbose=T, save_pred=T))
```

```{r}
xgb_rs_1_3_bis %>% collect_metrics()
```

```{r}
fit_workflow_1_3_bis <- fit(final_wf_xgb_1_3_bis, valgan_ml_train_60_120)
```


##Validation test
```{r}
final_res_1_3_bis <- final_wf_xgb_1_3_bis %>% 
  last_fit(valgan_split_60_120)  
```

```{r}
final_res_1_3_bis %>% collect_metrics()
```

```{r}
final_res_predictions_1_3_bis <- final_res_1_3_bis %>% 
  collect_predictions() %>%
  rename(AUC_pred = .pred) %>%
  mutate (bias_rel = (AUC_pred - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)


rmarkdown::paged_table(as.data.frame(final_res_predictions_1_3_bis %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```









Estimating AUC using ML algorithms on an external database (98 Caldés patients and 98 Chen patients)

#Test 1: 98 patients from the Caldés model (GFR between 60 and 120 mL/min, 900 mg/day)

##Data_set
```{r}
library(readxl)
data_normo_renaux_Caldés <- read_excel("./data/data_60_120_Caldés.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))

```

##Filter the 1st and 99th percentiles
```{r}
quantiles <- quantile(data_normo_renaux_Caldés$auc, probs = c(0.01, 0.99))

valgan_60_120_test_1 <- data_normo_renaux_Caldés %>%
  filter(auc > quantiles[1], auc < quantiles[2])
```

```{r}
skim(valgan_60_120_test_1)
```


##Prediction with the 2-samples algorithm (C4 and C12 + Clcr)
```{r}
predictions_1_2 <- predict(fit_workflow_1_2, valgan_60_120_test_1)
```

```{r}
valgan_60_120_test_1$AUC_pred_2_points <- predictions_1_2$.pred
```

```{r}
final_predictions_1_2 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_pred_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_1_2 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```


## Prediction with the 3-samples algorithm (C3, C4, and C12 + Clcr)
```{r}
predictions_1_3 <- predict(fit_workflow_1_3, valgan_60_120_test_1)
```

```{r}
valgan_60_120_test_1$AUC_pred_3_points <- predictions_1_3$.pred
```

```{r}
final_predictions_1_3 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_pred_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_1_3 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```


## Prediction with the 3-samples algorithm (C3, C4, and C6 + Clcr)
```{r}
predictions_1_3_bis <- predict(fit_workflow_1_3_bis, valgan_60_120_test_1)
```

```{r}
valgan_60_120_test_1$AUC_pred_3_points_bis <- predictions_1_3_bis$.pred
```

```{r}
final_predictions_1_3_bis <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_pred_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_1_3_bis %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```



#Test 2: 98 patients from the Chen et al. model (GFR between 60 and 120 mL/min, 900 mg/day)
## Data_set
```{r}
library(readxl)
data_normo_renaux_Chen <- read_excel("./data/data_60_120_Chen.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))
```

## Filter the 1st and 99th percentiles
```{r}
quantiles <- quantile(data_normo_renaux_Chen$auc, probs = c(0.01, 0.99))

valgan_60_120_test_2 <- data_normo_renaux_Chen %>%
  filter(auc > quantiles[1], auc < quantiles[2])
```


## Prediction with the 2-samples algorithm (C4 and C12 + Clcr)
```{r}
predictions_2_2 <- predict(fit_workflow_1_2, valgan_60_120_test_2)
```

```{r}
valgan_60_120_test_2$AUC_pred_2_points <- predictions_2_2$.pred
```

```{r}
final_predictions_2_2 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_pred_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_2_2 %>% summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```


## Prediction with the 3-samples algorithm (C3, C4, and C12 + Clcr)
```{r}
predictions_2_3 <- predict(fit_workflow_1_3, valgan_60_120_test_2)
```

```{r}
valgan_60_120_test_2$AUC_pred_3_points <- predictions_2_3$.pred
```

```{r}
final_predictions_2_3 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_pred_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_2_3 %>% summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```


## Prediction with the 3-samples algorithm (C3, C4, and C6 + Clcr)
```{r}
predictions_2_3_bis <- predict(fit_workflow_1_3_bis, valgan_60_120_test_2)
```

```{r}
valgan_60_120_test_2$AUC_pred_3_points_bis <- predictions_2_3_bis$.pred
```

```{r}
final_predictions_2_3_bis <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_pred_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(final_predictions_2_3_bis %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```









Bayesian prediction using the Vezina and Lalagkas models on the 98 patients simulated from the Caldes model (valgan_60_120_test_1)

#Prediction with the Vezina et al. model
## 2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_1))

for(i in 1:nrow(valgan_60_120_test_1)) {
  conc_time_4 <- valgan_60_120_test_1$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_1$conc_time_12[i]
  Clcr <- valgan_60_120_test_1$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_1$AUC_mapb_Veniza_2_points <- auc_estimated

prediction_mapb_Veniza_2_points_Ca_60_120 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_2_points_Ca_60_120 %>% summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```


## 3 samples (C3, C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_1))

for(i in 1:nrow(valgan_60_120_test_1)) {
  conc_time_3 <- valgan_60_120_test_1$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_1$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_1$conc_time_12[i]
  Clcr <- valgan_60_120_test_1$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_1$AUC_mapb_Veniza_3_points <- auc_estimated

prediction_mapb_Veniza_3_points_Ca_60_120 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_Ca_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```


## 3 samples (C3, C4 et C6)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_1))

for(i in 1:nrow(valgan_60_120_test_1)) {
  conc_time_3 <- valgan_60_120_test_1$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_1$conc_time_4[i]
  conc_time_6 <- valgan_60_120_test_1$conc_time_6[i]
  Clcr <- valgan_60_120_test_1$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 6, DV = conc_time_6) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_1$AUC_mapb_Veniza_3_points_bis <- auc_estimated

prediction_mapb_Veniza_3_points_bis_Ca_60_120 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_bis_Ca_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```


#Prediction with the Lalagkas model 
## 2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_1))

for(i in 1:nrow(valgan_60_120_test_1)) {
  conc_time_4 <- valgan_60_120_test_1$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_1$conc_time_12[i]
  Clcr <- valgan_60_120_test_1$Clcr[i]
  
  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_1$AUC_mapb_Lalagkas_2_points <- auc_estimated

prediction_mapb_Lalagkas_2_points_Ca_60_120 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_2_points_Ca_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```


## 3 samples (C3, C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_1))

for(i in 1:nrow(valgan_60_120_test_1)) {
  conc_time_3 <- valgan_60_120_test_1$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_1$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_1$conc_time_12[i]
  Clcr <- valgan_60_120_test_1$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_1$AUC_mapb_Lalagkas_3_points <- auc_estimated

prediction_mapb_Lalagkas_3_points_Ca_60_120 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_Ca_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```


## 3 samples (C3, C4 et C6)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_1))

for(i in 1:nrow(valgan_60_120_test_1)) {

  conc_time_3 <- valgan_60_120_test_1$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_1$conc_time_4[i]
  conc_time_6 <- valgan_60_120_test_1$conc_time_6[i]
  Clcr <- valgan_60_120_test_1$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 6, DV = conc_time_6) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl

  auc_estimated[i] <- AUC
}

valgan_60_120_test_1$AUC_mapb_Lalagkas_3_points_bis <- auc_estimated

prediction_mapb_Lalagkas_3_points_bis_60_120 <- valgan_60_120_test_1 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_bis_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```









Bayesian prediction by the Vezina and Lalagkas model on the 98 patients simulated from the Chen model (valgan_60_120_test_2)

#Prediction with the Vezina model
## 2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_2))

for(i in 1:nrow(valgan_60_120_test_2)) {=
  conc_time_4 <- valgan_60_120_test_2$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_2$conc_time_12[i]
  Clcr <- valgan_60_120_test_2$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_2$AUC_mapb_Veniza_2_points <- auc_estimated

prediction_mapb_Veniza_2_points_Ch_60_120 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_2_points_Ch_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```


## 3 samples (C3, C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_2))

for(i in 1:nrow(valgan_60_120_test_2)) {
  conc_time_3 <- valgan_60_120_test_2$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_2$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_2$conc_time_12[i]
  Clcr <- valgan_60_120_test_2$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
     obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_2$AUC_mapb_Veniza_3_points <- auc_estimated

prediction_mapb_Veniza_3_points_Ch_60_120 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_Ch_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```


## 3 samples (C3, C4 et C6)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_2))

for(i in 1:nrow(valgan_60_120_test_2)) {
  conc_time_3 <- valgan_60_120_test_2$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_2$conc_time_4[i]
  conc_time_6 <- valgan_60_120_test_2$conc_time_6[i]
  Clcr <- valgan_60_120_test_2$Clcr[i]

  my_est <- model_Vezina %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 6, DV = conc_time_6) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_2$AUC_mapb_Veniza_3_points_bis <- auc_estimated

prediction_mapb_Veniza_3_points_bis_Ch_60_120 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Veniza_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Veniza_3_points_bis_Ch_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```


#Prédiction avec modèle de Lalagkas
## 2 samples (C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_2))

for(i in 1:nrow(valgan_60_120_test_2)) {
  conc_time_4 <- valgan_60_120_test_2$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_2$conc_time_12[i]
  Clcr <- valgan_60_120_test_2$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_2$AUC_mapb_Lalagkas_2_points <- auc_estimated

prediction_mapb_Lalagkas_2_points_Ch_60_120 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_2_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_2_points_Ch_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```


## 3 samples (C3, C4 et C12)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_2))

for(i in 1:nrow(valgan_60_120_test_2)) {
  conc_time_3 <- valgan_60_120_test_2$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_2$conc_time_4[i]
  conc_time_12 <- valgan_60_120_test_2$conc_time_12[i]
  Clcr <- valgan_60_120_test_2$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 12, DV = conc_time_12) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_2$AUC_mapb_Lalagkas_3_points <- auc_estimated

prediction_mapb_Lalagkas_3_points_Ch_60_120 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_Ch_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)),
n= n())))
```


## 3 samples (C3, C4 et C6)
```{r}
auc_estimated <- numeric(length = nrow(valgan_60_120_test_2))

for(i in 1:nrow(valgan_60_120_test_2)) {
  conc_time_3 <- valgan_60_120_test_2$conc_time_3[i]
  conc_time_4 <- valgan_60_120_test_2$conc_time_4[i]
  conc_time_6 <- valgan_60_120_test_2$conc_time_6[i]
  Clcr <- valgan_60_120_test_2$Clcr[i]

  my_est <- model_Lalagkas %>%
    adm_rows(time = 0, amt = 900, ii = 24, ss = 1) %>%
    obs_rows(time = 3, DV = conc_time_3) %>%
    obs_rows(time = 4, DV = conc_time_4) %>%
    obs_rows(time = 6, DV = conc_time_6) %>%
    add_covariates(Clcr = Clcr) %>%
    mapbayest()
  
  est_cl <- get_param(my_est, "CL")
  AUC <- my_est$mapbay_tab$amt / est_cl
  
  auc_estimated[i] <- AUC
}

valgan_60_120_test_2$AUC_mapb_Lalagkas_3_points_bis <- auc_estimated

prediction_mapb_Lalagkas_3_points_bis_Ch_60_120 <- valgan_60_120_test_2 %>% 
  mutate (bias_rel = (AUC_mapb_Lalagkas_3_points_bis - auc)/auc,
          bias_rel_square = bias_rel * bias_rel)

rmarkdown::paged_table(as.data.frame(prediction_mapb_Lalagkas_3_points_bis_Ch_60_120 %>% 
summarise(relative_bias = mean(bias_rel), 
relative_rmse = sqrt(mean(bias_rel_square)),
biais_out_20percent = mean(!between(bias_rel,-0.2, 0.2)), 
nb_out_20percent = sum(!between(bias_rel,-0.2, 0.2)), 
n= n())))
```
